Roster Review (Generic)

### 2019-06-01 rosterReview_generic.Rmd
Moved more munging code to helper, finished a few to-dos

```{r}
force <- FALSE
force_all <- FALSE
batter_file <- NULL
pitcher_file <- NULL

@@

```{r}
#TODO move to helper
rosters %>% 
  filter(type != 'NA', team != 'Free Agent') %>%
  group_by(type) %>% 
  summarize(adj = median(z_sum)) -> z_sum_adj

rosters <- rosters %>% 
  filter(!type == 'NA') %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))

position_columns <- rosters %>%
    select(starts_with("eligible_positions")) %>%
    colnames()

rosters %>%
  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
  mutate(positions = gsub('NA', '', positions)) %>%
  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
  select(-(starts_with("eligible_positions"))) -> rosters
```

```{r}
#TODO abstract some of these views
#FIXME some join issues here
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, display_position, type, zar) %>% 
  View()
```

@@

rosters %>% 
  filter(grepl("Plouffe|theriverbrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("deGrom|Lucchesi",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters %>% 
  filter(!grepl("Free Agent",team),
  grepl("CF",positions)
       ) %>%
  ggplot(aes(x=team,y=zar,color=type)) +
  #geom_boxplot() +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

>>>>

```{r}
force <- TRUE
force_all <- FALSE
batter_file <- NULL
pitcher_file <- NULL

@@

```{r}
#TODO abstract some of these views
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, positions, type, zar) %>% 
  View()
```

@@

rosters %>% 
  filter(grepl("process|Dorn",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Cain|Price|Romo|Trout|Whitley|Claudio",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters %>% 
  filter(!grepl("Free Agent",team)
  #        ,
  # grepl("CF",positions)
       ) %>%
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_boxplot() +
  # geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO move to separate research
#FIXME where is Robinson Chirinos?

rosters_by_position <- row_per_position(rosters)

rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos

ggplotly(team_pos)
```
